\vspace{-13mm}\includegraphics[width=15mm,scale=3]{../images/IST_Logo.png} \\ {\fontsize{24}{16}Detection of Li in Technological Materials through Nuclear Reactions} \vspace{-5mm}

### 2024-01-20 text/paper/paper.tex
Paper.tex
fix: .bib
ready
Final Paper

\usepackage[style=numeric]{biblatex} % Choose your desired citation style
\addbibresource{../references/prop.bib} % Specify your .bib file

@@

\begin{multicols}{2}

\section{Main Goal}
    \label{sec:maingoal}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.5]{../../images/TT_21_Chn0.png}
    \captionof{figure}{Detector 0 spectrum fit with triple gaussian}
\end{center}

@@

\begin{center}
    \label{alfa_peaks}
    \centering
    \includegraphics[scale = 0.3]{../../images/AlphaPeaks.jpeg}
    \captionof{figure}{Theoretical energy values of the two alphas}
\end{center}

@@

With this we get:

Implanted Sample: $N\Delta x = 9.25\times 10^{16}$ atoms per cm$^2$\\
$\ce{LiAlO2}$: $N\tau_i=4.31\times10^{17}$ atoms per cm$^2$\\
$\ce{LiF}$: $N\tau_i=1.15\times10^{18}$ atoms per cm$^2$

For comparison:
$\ce{LiAlO2}$: $N\Delta x=2.15\times10^{19}$ atoms per cm$^2$\\
$\ce{LiF}$: $N\Delta x=5.71\times10^{19}$ atoms per cm$^2$\\

@@

\printbibliography
\nocite{*}

>>>>

\usepackage[backend=biber, style=numeric]{biblatex}
\addbibresource{paper.bib}

@@

\begin{multicols}{2}
\small
\section{Main Goal}
    \label{sec:maingoal}

@@

\begin{center}
    \label{TT_21}
    \centering
    \includegraphics[scale = 0.5]{../../images/TT_21_Chn0.jpeg}
    \captionof{figure}{Detector 0 spectrum fit with triple gaussian}
\end{center}

@@

\begin{center}
    \label{alfa_peaks}
    \centering
    \includegraphics[scale = 0.28]{../../images/AlphaPeaks.jpeg}
    \captionof{figure}{Theoretical energy values of the two alphas}
\end{center}

@@

With this we get:
\begin{itemize}[noitemsep, left=1cm]
    \item Implanted Sample: $N\Delta x = 9.25\times 10^{16}$ atoms per cm$^2$\\
    \item $\ce{LiAlO2}$: $N\tau_i=4.31\times10^{17}$ atoms per cm$^2$\\
    \item $\ce{LiF}$: $N\tau_i=1.15\times10^{18}$ atoms per cm$^2$
\end{itemize}

For comparison:
\begin{itemize}[noitemsep, left=1cm]
\item $\ce{LiAlO2}$: $N\Delta x=2.15\times10^{19}$ atoms per cm$^2$\\
\item $\ce{LiF}$: $N\Delta x=5.71\times10^{19}$ atoms per cm$^2$\\
\end{itemize}

@@

\nocite{*}
\printbibliography
